Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
update additional ref to tab:tickAssign

\newcommand{\dnote}[1]{\textcolor{darkpurple}{Dom: #1}}
\newcommand{\mnote}[1]{\textcolor{darkgreen}{Mistral: #1}}
\newcommand{\anote}[1]{\textcolor{red}{Andy: #1}}

@@

The pairwise permutation $u \bowtie v$ takes two vectors and builds the matrix
where the rows are all possible $n$-vectors generated by
non-deterministic picking each $i^{th}$ entry from either the
$i^{th}$ entry in $u$ or the $i^{th}$ entry in $j$. For example:
%
\begin{equation*}
\vthreeh{0}{1}{2} \bowtie \vthreeh{3}{4}{5} =
\left[
\setlength{\arraycolsep}{0.42em}
\begin{array}{cccccccc}
0 & 0 & 0 & 0 & 3 & 3 & 3 & 3 \\ 
1 & 1 & 4 & 4 & 1 & 1 & 4 & 4 \\
2 & 5 & 2 & 5 & 2 & 5 & 2 & 5
\end{array}
\right]
% \\
%\setlength{\arraycolsep}{0.5em}
%\left[\begin{array}{ccc}
%0 & 1 & 2 \\
%0 & 1 & 5 \\
%0 & 4 & 2 \\
%0 & 4 & 5 \\
%3 & 1 & 2 \\
%3 & 1 & 5 \\
%3 & 4 & 2 \\
%3 & 4 & 5
%\end{array}
%\right]
\end{equation*}
%
The $2^n$ unique choices for $\bowtie$ on $n$-vectors
corresponds to taking all bit-strings of length $n$ and
selecting from $u$ for $1$ and $v$ for $0$. Thus, we can
defined the pairwise permutation matrix as:
%
\begin{align*}
(u \bowtie v)_{i,j} & = b_{i,j} u_j + \neg b_{i,j} v_j
\end{align*}
%
where $b$ is a logical matrix where $b_{i,j}$ is the $j$-th bit of the integer
$i - 1$.
%%
\dnote{I didn't understand mistral's description of unification
wrt to $\tensor$. I can't work it out either! Mistral have another
go given my above explanation}
\end{definition}

@@

If the statement meets the stencil critera but the inference process cannot determine an exact stencil for a statement it will instead produce an upper (\term{atMost}) and lower (\term{atLeast}) bound. The number of exact and inexact stencils are shown in columns three and four of Figure \ref{fig:tickAssign}. We can see that our stencil language is capable of precisely specifying the overwhelming majority of stencils. Most of the inexact stencils apply to some form of data copying. For example (taken from E3MG):
\begin{minted}{fortran}
!- stencil atLeast, readOnce, irreflexive(dims=2), (reflexive(dim=1)) :: sfda
!- stencil atMost, readOnce, (forward(depth=8, dim=2))*(reflexive(dim=1)) :: sfdt
ZZ1(I,J) = SFDT(I,J+8)
\end{minted}

>>>>

\newcommand{\todo}[1]{\textcolor{blue}{Dom: #1}}
\newcommand{\dnote}[1]{\textcolor{darkpurple}{Dom: #1}}
\newcommand{\mnote}[1]{\textcolor{darkgreen}{Mistral: #1}}
\newcommand{\anote}[1]{\textcolor{red}{Andy: #1}}

@@

The pairwise permutation $u \bowtie v$ takes two vectors and builds the matrix
where the rows are all possible $n$-vectors generated by
non-deterministic picking each $i^{th}$ entry from either the
$i^{th}$ entry in $u$ or the $i^{th}$ entry in $j$. For example:
%
\begin{equation*}
\vthreeh{0}{1}{2} \bowtie \vthreeh{3}{4}{5} =
\left[
\setlength{\arraycolsep}{0.42em}
\begin{array}{cccccccc}
0 & 0 & 0 & 0 & 3 & 3 & 3 & 3 \\ 
1 & 1 & 4 & 4 & 1 & 1 & 4 & 4 \\
2 & 5 & 2 & 5 & 2 & 5 & 2 & 5
\end{array}
\right]
% \\
%\setlength{\arraycolsep}{0.5em}
%\left[\begin{array}{ccc}
%0 & 1 & 2 \\
%0 & 1 & 5 \\
%0 & 4 & 2 \\
%0 & 4 & 5 \\
%3 & 1 & 2 \\
%3 & 1 & 5 \\
%3 & 4 & 2 \\
%3 & 4 & 5
%\end{array}
%\right]
\end{equation*}
%
The $2^n$ unique choices for $\bowtie$ on $n$-vectors
corresponds to taking all bit-strings of length $n$ and
selecting from $u$ for $1$ and $v$ for $0$. Thus, we can
defined the pairwise permutation matrix as:
%
\begin{align*}
(u \bowtie v)_{i,j} & = b_{i,j} u_j + \neg b_{i,j} v_j
\end{align*}
%
where $b$ is a logical matrix where $b_{i,j}$ is the $j$-th bit of the integer
$i - 1$.
%%
\dnote{I didn't understand mistral's description of unification
wrt to tensor. I can't work it out either! Mistral have another
go given my above explanation}
\end{definition}

@@

If the statement meets the stencil critera but the inference process cannot determine an exact stencil for a statement it will instead produce an upper (\term{atMost}) and lower (\term{atLeast}) bound. The number of exact and inexact stencils are shown in columns three and four of Figure \ref{tab:tickAssign}. We can see that our stencil language is capable of precisely specifying the overwhelming majority of stencils. Most of the inexact stencils apply to some form of data copying. For example (taken from E3MG):
\begin{minted}{fortran}
!- stencil atLeast, readOnce, irreflexive(dims=2), (reflexive(dim=1)) :: sfda
!- stencil atMost, readOnce, (forward(depth=8, dim=2))*(reflexive(dim=1)) :: sfdt
ZZ1(I,J) = SFDT(I,J+8)
\end{minted}
